\documentclass{article} % For LaTeX2e
% We will use NIPS submission format
\usepackage{nips13submit_e,times}
% for hyperlinks
\usepackage{hyperref}
\usepackage{placeins}
\usepackage{url}
% For figures
\usepackage{graphicx} 
% math packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsopn}
\usepackage{ifthen}
\usepackage{natbib}
\usepackage{caption}
\usepackage{subcaption}

\title{Project-I by Group Rome}
\author{
\fontsize{8}{8}\selectfont{Cimen Gokcen}\\
\fontsize{8}{8}\selectfont{EPFL} \\
\fontsize{8}{8}\selectfont{\texttt{gokcen.cimen@epfl.ch}} \\
\And
\fontsize{8}{8}\selectfont{Petrescu Viviana}\\
\fontsize{8}{8}\selectfont{EPFL} \\
\fontsize{8}{8}\selectfont{\texttt{viviana.petrescu@epfl.ch}} \\
\And
\fontsize{8}{8}\selectfont{Angelopoulos Vasileios} \\
\fontsize{8}{8}\selectfont{EPFL} \\
\fontsize{8}{8}\selectfont{\texttt{vasileios.angelopoulos@epfl.ch}} \\
}

\nipsfinalcopy 

\begin{document}

\maketitle

\begin{abstract}
This report presents conclusions after experimenting on two tasks, classification and regression. We process the given training data, investigate baseline methods and present our results here. For the regression task all of the methods perform similarly, but we chose to present the results using ridge regression. Moreover, we applied polynomial feature transformations, resulting in possible over-fitting of the model. For the classification part, both logistic regression and its penalized version performed equally well, but the feature transformations that we tried did not improve the result even more.
\end{abstract}

\section{Regression}
\input{Regression}

\section{Classification}
\input{Classification}

\subsubsection*{Acknowledgments}
We would like to thank the course teaching assistants that helped us a lot during this project preparation, not only during the exercise session, but also at their office hours. Furthermore, the help that our teacher Mohammad Emtiyaz Khan offered us was very  important, and we would want to thank him, too. All of the code used and submitted along with this report was written by equally by all of our group members.

\end{document}
